Temperature sensor calibration
========================================================


```{r loaddata, cache=TRUE}
foo=read.table("data/20130311.txt", sep=";");
logdata=data.frame(
  idx=c(1:length(foo$V1)),
  t_hyt=foo$V1,
  h_hyt=foo$V2,
  t_an1=foo$V4,
  t_an2=foo$V5
  )
mintemp=min(logdata$t_hyt, logdata$t_an1, logdata$t_an2)
maxtemp=max(logdata$t_hyt, logdata$t_an1, logdata$t_an2)
tmpframe=data.frame(logdata$t_an1, logdata$t_an2);
t_mean_analog = rowMeans(tmpframe);
```

# Visual inspection of dataset

```{r visual, dependson="loaddata", cache=TRUE, fig.width=7, fig.height=6}
plot(logdata$idx, logdata$t_hyt, type="l", col=1, xlab="Index", 
     ylab="Temperature [deg C]", ylim=c(mintemp, maxtemp));
lines(logdata$idx, logdata$t_an1, type="l", col=2);
lines(logdata$idx, logdata$t_an2, type="l", col=3);
legend(3000, 26.2, c("HYT271", "Analog 1", "Analog 2"), col=c(1:3), lty=1)
```

```{r summary, dependson="loaddata"}
summary(logdata)
```

# Fitting a linear model

Assumption: The real temperature is the mean of the two analog temperature sensors.
TODO: Ensure proper calibration of both sensors.

```{r linmodel, dependson="loaddata", cache=TRUE}
lm1 = lm(logdata$t_hyt ~ t_mean_analog)
summary(lm1)
plot(lm1)
cat(paste("The offset of the linear model is ", lm1$coefficients[1]))
```


## Using loess to smoothen values.
The t_mean_analog factor seems odd - this should be one. Hypothesis: The discretization of the sensor values interferes with the model. 

```{r smooth, dependson="loaddata", cache=TRUE}
loess_hyt=loess(logdata$t_hyt ~ logdata$idx, span=0.1)
plot(logdata$idx, logdata$t_hyt, type="o", col=1, xlab="Index", 
     ylab="Temperature [deg C]", ylim=c(mintemp, maxtemp), pch=19, cex=0.2);
lines(logdata$idx, loess_hyt$fitted, type="l", col=3, cex=10);

loess_analog=loess(t_mean_analog ~ logdata$idx, span=0.1)
lines(logdata$idx, t_mean_analog, type="o", col=2, pch=19, cex=0.2);
lines(logdata$idx, loess_analog$fitted, type="l", col=3, cex=2);
legend(3000, 26.2, c("HYT271", "Analog Mean"), col=c(1:2), lty=1)
lm3=lm(loess_hyt$fitted ~ loess_analog$fitted)
summary(lm3)
qqplot(logdata$t_hyt, t_mean_analog)
abline(c(lm3$coeff[1], 1))
```

## FOo0

```{r foo, dependson="loaddata"}
s_t_hyt = sort(logdata$t_hyt)
s_t_analog= sort(t_mean_analog)
lm4=lm(s_t_hyt ~ s_t_analog)
summary(lm4)
qqplot(logdata$t_hyt, t_mean_analog)
abline(c(abs(lm4$coeff[1]), 1))
```

## Using simpler median statistics 

```{r median, dependson="loaddata", cache=TRUE}
m_hyt=quantile(logdata$t_hyt, probs=0.5)
m_analog=quantile(t_mean_analog, probs=0.5)
offset = m_analog - m_hyt
cat(paste("The offset between HYT and the mean analog sensor is ", offset))
qqplot(logdata$t_hyt, t_mean_analog)
abline(c(offset, 1))
```
